### 2016-07-08 intro.tex
intro clean up

First, we note that the security notion forbids~$A$ to win if it
outputs $x^* \in \{x_1,x_2,\ldots,x_q\}$, even if one of these was a
false positive.
\jnote{We discussed this on the phone, but let me
put it in writing here. I think this is actually a reasonable choice
because it captures the notion that ``even after finding some false
positives, it remains hard to find additional false positives.''
Note that in practice finding false positives is ``easy'' since
$\epsilon$ might be $1/1000$ rather than negligible.}
\tsnote{For me the question is: is security violated once the first FP is found, or
the second?  My answer, which is in line with the traditional
soundness notion, is that the first FP is a security violation
even if finding it isn't ``hard'' by cryptographic standards.
But I do appreciate your point.  A natural goal is to say that, in some sense,
\emph{adaptivity doesn't make it any easier} to find a FP.  Adapting
to what, though?  In the traditional notion, $x$~is picked before the
coins of~$\mathbf{B}_1$ are flipped, i.e., before the hash functions
are sampled.  The direct non-adaptive generalization is to say that
$x_1,x_2,\ldots,x_q$ are all picked up front.  The direct
\emph{adaptive} generalization would allow $x_1,x_2,\ldots,x_q$ to
depend in the coins of~$\mathbf{B}_1$, i.e., the hash functions.  The
NY definition captures only indirect dependence: adversaries that can adapt to set-membership queries,
but \emph{not} (directly) to the input-output behaviors of the hash
functions.  The three notions I've proposed in Figure 1 cover a
spectrum of adaptivity: the first is adapting to set-membership queries
only, the second to those and hash input-output behavior, the third to
set-membership queries and full knowledge of the hash functions.  Each
has it's own associated (informal) security interpretation.}

\tsnote{Perhaps a more obvious way to capture the idea that ``finding
  some FPs doesn't help find additional ones'' is to parameterize my notion(s) with a number~$f$, and say
that that the adversary wins iff it outputs~$f$ FPs (these may have
been previously queried to the set-membership oracle).
Note that in the ROM (and probably in practice) finding~$f>1$ FPs will
require~$f$ times the work.  Right?} \tsnote{FYI: this is how MAC security against multiple forgeries is defined.  See \texttt{https://eprint.iacr.org/2006/095.pdf} for details.}
%\tsnote{Here's an off-the-wall idea.  What if the basic FP security
%notion gave the adversary an oracle for set-membership (and the hash functions, depending on the setting), and after interacting with these
%it is challenged with either $x_0$ or $x_1$, where $x_0$ is a random
%point from the set of non-FPs, and $x_1$ is a random point from the
%set of FPs?  (No oracles after being challenged.)  The adversary has
%to decide which it received.}

Second, we note that the NY syntax does not capture the size of~$M$
as a parameter; \jnote{I think this is also reasonable; typically
security is defined without regard for efficiency} \tsnote{My
complaint isn't about efficiency. It's about the fact that, by not
including $|M|$ in the definition, the trivial scheme I give (just
below) is allowed, and is secure.  Anyway, as I say at the end of
this paragraph, this is a small(er) complaint than what follows}.
\jnote{I would say that the trivial scheme \emph{is} secure!} The
surrounding text does say that $\mathbf{B}_1$ ``outputs a compressed
representation [of $\mathcal{S}$] $\mathbf{B}_1(\mathcal{S})=M$''
but what exactly this means is never addressed.  The formal syntax
admits $\mathbf{B}_1(\mathcal{S})=\mathcal{S}$ and
$\mathbf{B}_2(\mathcal{S},x)=1 \Leftrightarrow x \in \mathcal{S}$,
which is also trivially secure by their definition.  These are both
small, but important complaints.  But a larger complaint, and one
that is much harder to see, is that that it is not clear that the NY
formalism actually captures real world Bloom filters.

@@

\jnote{FWIW, I think the classical description of Bloom filters has
the same problem. I.e., if the hash functions are not fixed, then
their description should be counted as part of the length of the
data structure. On the other hand, if they are fixed, then the
false-positive rate is not well-defined (since there is no
probability space to speak of). So in that sense, NY just carried
over the problem from the classical literature.}
\tsnote{One can suggest that it \emph{should} be counted in the classical
  description, but the fact is that it isn't :)  And in the 30+ years
  since the original paper, no one saw fit to correct this?  From an
  algorithmic perspective, I think the classical approach makes
  sense.  The questions being answered are: how many bits do I need to
  store a representation of the set for a given FP rate, and how does this compare to the
  combinatorially computed lower-bound?  The description length of the
hash functions may be bigger or smaller, but the number of bits you
need to hold the set representation is independent of that.  (Imagine
that you have long random bitstrings in the set~$\mathcal{S}$.  Then
whether your hash functions simply truncate, or they are random
oracles, the size of the representation as a function of the target FP
rate doesn't change.  Yet the description lengths of the hash
functions are drastically different.)}

@@

There are applications in which the proposed Bloom filter instantiations do
use secretly keyed hash functions, e.g. $h_j(x) = (f(K_0,x) + j\cdot
g(K_1,x))\bmod m$, where $j\in[1,k]$, $m$ is the number of bits in
the array, and where $f,g$ are PRFs keyed by secrets $K_0,K_1$.
This particular ``encrypted Bloom filter'' instantiation was
suggested for use in efficient linking of records across separate
medical record databases~\cite{xxx}.  (It was subsequently shown not
to be secure by Niedermeier et al.~\cite{xxx}, where a clever use of
frequency analysis recovered the last names of patients given access
only to the Bloom filter array.)
%\tsnote{This shows that false-positive security and privacy (whatever it is) are orthogonal,
%since I'm pretty sure this ``encrypted'' bloom filter resists FPs.})
In any case, it is clear that the NY definition does not capture the
most widely used applications of Bloom filters, e.g. CDN summary
caches, P2P network routing algorithms, etc. \tsnote{Could also
point out that their positive results use constructions that have
secret keys, and these are unlikely to be of any use in major
applications like CDNs or P2P networks.  But maybe the horse is
sufficiently beaten by now...}

@@

We generalize this syntax to hash-based filters that are mutable
\jnote{I find ``mutable'' a slightly awkward term,  maybe because it
makes me think of mutability in the context of programming
languages. In much data structures literature, this is called the
``dynamic'' case, in contrast to the ``static'' case.} \tsnote{I
adopted this term after reading it in some bloom filter
paper(s). Ironically, I liked it for the same reason you think it is
awkward :)  My PL association to the term is that an immutable object
is one whose state cannot be modified after it is created, and a
mutable object is the opposite.  But I don't really care too much.}, in the sense
that they allow for updating of the representation. This allows us
to capture counting Bloom filters, spectral Bloom filters, stable
Bloom filters, count-min sketches, and other compact set
representation data structures...

>>>>

First, we note that the security notion forbids~$A$ to win if it outputs $x^* \in \{x_1,x_2,\ldots,x_q\}$, even if one of these was a false positive.  On one hand, this notion is unsatisfying because it would not say that an attacker wins by creating (say) a bogus email address, and then observing that it passes a spam filter that is based on a Bloom filter represention of a whitelist.\footnote{This is one of the motivating examples from NY.}  The attacker is only allowed to win if it finds a false-positive that it has not verified.  On the other hand, the NY notion does seem to capture the intuition that finding additional false positives does not become easier as more are learned.  Our notions will address both sides of this discussion.
%
%\jnote{We discussed this on the phone, but let me put it in writing here. I think this is actually a reasonable choice because it captures the notion that ``even after finding some false positives, it remains hard to find additional false positives.'' Note that in practice finding false positives is ``easy'' since $\epsilon$ might be $1/1000$ rather than negligible.}
%
%\tsnote{For me the question is: is security violated once the first FP is found, or the second? My answer, which is in line with the traditional soundness notion, is that the first FP is a security violation even if finding it isn't ``hard'' by cryptographic standards. But I do appreciate your point.  A natural goal is to say that, in some sense, \emph{adaptivity doesn't make it any easier} to find a FP.  Adapting to what, though? In the traditional notion, $x$~is picked before the coins of~$\mathbf{B}_1$ are flipped, i.e., before the hash functions are sampled.  The direct non-adaptive generalization is to say that $x_1,x_2,\ldots,x_q$ are all picked up front.  The direct \emph{adaptive} generalization would allow $x_1,x_2,\ldots,x_q$ to depend in the coins of~$\mathbf{B}_1$, i.e., the hash functions.  The NY definition captures only indirect dependence: adversaries that can adapt to set-membership queries, but \emph{not} (directly) to the input-output behaviors of the hash functions.  The three notions I've proposed in Figure 1 cover a spectrum of adaptivity: the first is adapting to set-membership queries only, the second to those and hash input-output behavior, the third to set-membership queries and full knowledge of the hash functions.  Each has it's own associated (informal) security interpretation.}
%\tsnote{Perhaps a more obvious way to capture the idea that ``finding some FPs doesn't help find additional ones'' is to parameterize my notion(s) with a number~$f$, and say that that the adversary wins iff it outputs~$f$ FPs (these may have been previously queried to the set-membership oracle). Note that in the ROM (and probably in practice) finding~$f>1$ FPs will require~$f$ times the work.  Right?} 
%
%\tsnote{FYI: this is how MAC security against multiple forgeries is defined.  See \texttt{https://eprint.iacr.org/2006/095.pdf} for details.}

Second, we note that the NY syntax does not capture the size of~$M$ as a parameter; 
\jnote{I think this is also reasonable; typically security is defined without regard for efficiency} \tsnote{My complaint isn't about efficiency. It's about the fact that, by not including $|M|$ in the definition, the trivial scheme I give (just below) is allowed, and is secure.  Anyway, as I say at the end of
this paragraph, this is a small(er) complaint than what follows}.
\jnote{I would say that the trivial scheme \emph{is} secure!} 
\tsnote{Okay, well then we need some way to ``rule out'' the trivial solution.  Perhaps just in the text -- yes, the trivial scheme works, but it isn't interesting in practice. Also, in the concrete security bounds that we will prove, the size of the representation is going to come up, e.g.\ the number of bits in the BF array directly affect the FP rate.  Hence it makes sense to say things like ``an $(n,k,m)$-filter...'' where $m$ is the size of the representation.}
The surrounding text does say that $\mathbf{B}_1$ ``outputs a compressed representation [of $\mathcal{S}$] $\mathbf{B}_1(\mathcal{S})=M$'' but what exactly this means is never addressed.  The formal syntax admits $\mathbf{B}_1(\mathcal{S})=\mathcal{S}$ and $\mathbf{B}_2(\mathcal{S},x)=1 \Leftrightarrow x \in \mathcal{S}$, which is also trivially secure by their definition.  These are both small, but important complaints.  But a larger complaint, and one that is much harder to see, is that that it is not clear that the NY formalism actually captures real world Bloom filters.

@@

%\jnote{FWIW, I think the classical description of Bloom filters has the same problem. I.e., if the hash functions are not fixed, then their description should be counted as part of the length of the data structure. On the other hand, if they are fixed, then the false-positive rate is not well-defined (since there is no probability space to speak of). So in that sense, NY just carried over the problem from the classical literature.}
%
%\tsnote{One can suggest that it \emph{should} be counted in the classical description, but the fact is that it isn't :) And in the 30+ years since the original paper, no one saw fit to correct this? From an algorithmic perspective, I think the classical approach makes sense.  The questions being answered are: how many bits do I need to store a representation of the set for a given FP rate, and how does this compare to the combinatorially computed lower-bound? The description length of the hash functions may be bigger or smaller, but the number of bits you need to hold the set representation is independent of that.  (Imagine that you have long random bitstrings in the set~$\mathcal{S}$.  Then whether your hash functions simply truncate, or they are random oracles, the size of the representation as a function of the target FP rate doesn't change.  Yet the description lengths of the hash functions are drastically different.)}

@@

There are applications in which the proposed Bloom filter instantiations do use secretly keyed hash functions, e.g. $h_j(x) = (f(K_0,x) + j\cdot g(K_1,x))\bmod m$, where $j\in[1,k]$, $m$ is the number of bits in the array, and where $f,g$ are PRFs keyed by secrets $K_0,K_1$. This particular ``encrypted Bloom filter'' instantiation was suggested for use in efficient linking of records across separate medical record databases~\cite{xxx}.  (It was subsequently shown not to be secure by Niedermeier et al.~\cite{xxx}, where a clever use of frequency analysis recovered the last names of patients given access only to the Bloom filter array.)
In any case, it is clear that the NY definition does not capture the most widely used applications of Bloom filters, e.g. CDN summary caches, P2P network routing algorithms, etc. 
%\tsnote{Could also point out that their positive results use constructions that have secret keys, and these are unlikely to be of any use in major applications like CDNs or P2P networks.  But maybe the horse is sufficiently beaten by now...}

@@

We generalize this syntax to hash-based filters that are mutable,
%\jnote{I find ``mutable'' a slightly awkward term, maybe because it makes me think of mutability in the context of programming languages. In much data structures literature, this is called the ``dynamic'' case, in contrast to the ``static'' case.} 
%
%\tsnote{I adopted this term after reading it in some bloom filter paper(s). Ironically, I liked it for the same reason you think it is awkward :) My PL association to the term is that an immutable object is one whose state cannot be modified after it is created, and a mutable object is the opposite.  But I don't really care too much.}
in the sense
that they allow for updating of the representation. This allows us
to capture counting Bloom filters, spectral Bloom filters, stable
Bloom filters, count-min sketches, and other compact set
representation data structures...
